Long-term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-08-27 Article_B11/Article_B11_plain.tex
Commit 2024-08-27 07:11

\caption{Example scatter plot of the measured GHI and the reference clear sky irradiance in Thessaloniki for the year 2005. The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.}\label{fig:example-year}
\end{figure}

>>>>

\caption{Example scatter plot of the measured GHI and the reference clear sky irradiance in Thessaloniki for the year 2005. The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black. The reference green line goes through the origin with a slope of one.}\label{fig:example-year}
\end{figure}
